Hydra Battles and Cie

### 2021-07-07 doc/part-hydras.tex
Simplification of some definitions

The following class definition, parameterized with a type $A$, a binary relation \texttt{lt} on $A$, specifies that \texttt{lt} is a well-founded strict order. The reflexive closure of \texttt{lt}, (called \texttt{le}, for ``less  or equal than'') is a total decidable order, implemented through a comparison function \texttt{compare}.  The correctness of this function is expressed through Stdlib's type 
\texttt{Datatypes.CompareSpec}.

First, we import the definition of strict orders from
the library ~\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Classes.RelationClasses.html}{%
Classes.RelationClasses}, 
and the inductive specification of a comparison from
\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Init.Datatypes.html}{%
Init.Datatypes}.

\begin{Coqsrc}
Variable A: Type.

  Class StrictOrder (R : relation A) : Prop := {
    StrictOrder_Irreflexive :> Irreflexive R ;
    StrictOrder_Transitive :> Transitive R }.
\end{Coqsrc}

@@

@@

\begin{Coqsrc}
Class ON {A:Type}(lt: relation A)
      (compare : A -> A -> comparison)  :=
  {
  sto :> StrictOrder lt;
  wf : well_founded lt;
  compare_correct :
    forall alpha beta:A,
      CompareSpec (alpha=beta) (lt alpha beta) (lt beta alpha)
                  (compare alpha beta);
  }.
\end{Coqsrc}

>>>>

From the \coq{} user's point of view, an ordinal notation is
a structure allowing to compare two ordinals by computation, and proving by well-founded induction.

\subsubsection{The \texttt{Comparable class}}

The following class, contributed by Jérémy Damour and Théo Zimmermann, allows us to apply generic lemmas and tactics
about decidable strict orders.
The correctness of the comparison function is expressed through Stdlib's type 
\texttt{Datatypes.CompareSpec}.

@@

\begin{Coqsrc}
Class Comparable {A:Type} 
  (lt: relation A)
  (compare : A -> A -> comparison) :=
  {
  sto :> StrictOrder lt;
  compare_correct: forall a b,
      CompareSpec (a = b) (lt a b) (lt b a) (compare a b);
  }.
\end{Coqsrc}

\subsubsection{The \texttt{ON} class}

The following class definition, parameterized with a type $A$, a binary relation \texttt{lt} on $A$, specifies that \texttt{lt} is a well-founded strict order, provided with a correct comparison function.

@@

\begin{Coqsrc}
Class ON {A:Type}(lt: relation A)
      (compare : A -> A -> comparison)  :=
  {
  comp :> Comparable lt compare;
  wf : well_founded lt;
  }.
\end{Coqsrc}
